


% navyblue color for hyperlinks
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% PhD
%---------------------------------------------------------
  \cventry
    {PhD, Nutritional Sciences} % Degree
    {The University of Illinois at Urbana-Champaign} % Institution
    {Urbana, IL} % Location
    {Anticipated May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textit{Concentration}: Nutritional Epidemiology and Data Science}
         \item {Advisors: Dr. Anna Arthur, PhD ( \textcolor{navyblue}{{\underline{\href{mailto:aarthur4@kumc.edu}{aarthur4@kumc.edu}}}}), MPH, RD and Dr. Zeynep Madak-Erdogan, PhD ( \textcolor{navyblue}{\underline{\href{mailto:zmadake2@illinois.edu}{zmadake2@illinois.edu}}})}
         \item{Dissertation Committee: Dr. Anna Arthur, PhD, MPH, RD, Dr. Zeynep Madak-Erdogan, PhD, Dr. Sandra Rodriguez-Zas PhD, Dr. Rebecca Smith, PhD}
      \end{cvitems}
    }

%---------------------------------------------------------

%MS
%---------------------------------------------------------
  \cventry
    {M.S., Statistics} % Degree
    {The University of Illinois at Urbana-Champaign} % Institution
    {Urbana, IL} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 4.00}
      \end{cvitems}
    }

%---------------------------------------------------------

%HPRS
%---------------------------------------------------------
  \cventry
    {Scholar and Award Recipient} % Degree
    {The Robert Wood Johnson Foundation's Health Policy Research Scholars} % Institution
    {Urbana, IL} % Location
    {2020-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Health Policy Research Scholars is a national leadership program supported by the Robert Wood Johnson Foundation.} 
        \item{It supports scholars from diverse disciplines and backgrounds in applying and advocating for policy changes that improve health and equity.}
        \item{ Scholars receive interactive training in policy development and implementation.}
      \end{cvitems}
    }

%---------------------------------------------------------

%BS
%---------------------------------------------------------
  \cventry
    {B.S., Nutritional Science \textit{(Cum Laude)}} % Degree
    {The University of Maryland, College Park} % Institution
    {College Park, MD} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 3.83, Major GPA: 3.89}
        \item{Phi Kappa Phi Recognition}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
