
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {The Urban Institute} % Organization
    {500 L'Enfant Plaza SW
    Wash., DC} % Location
    {Jun. 2022 - Present \newline 20 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an R package (\textit{fiscal}) for computing fiscal health metrics for nonprofit organizations filing form 990 or form 990-EZ with the IRS.}
        \item {Mined, geocoded, and merged data from several public sources for a geospatial analysis of nonprofit density in the United States.}
        \item {Designed, created, and implemented a geospatial data dashboard using RShiny for visualizing nonprofit density in the U.S.}
        \item {Implemented the Agile/Scrum project management framework in all projects I led and collaborated on.}
        \item {Supervisor: Jesse Lecy ( \textcolor{navyblue}{\underline{\href{mailto:jlecy@urban.org}{jlecy@urban.org}}})}
      \end{cvitems}
    }


% GRA
%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {The University of Illinois at Urbana-Champaign \newline Division of Nutritional Sciences } % Organization
    {1201 W. Gregory Drive \newline
    240 ERML\newline Urbana, IL} % Location
    {Aug. 2018 - Present \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluate the role of dietary patterns on prognostically-relevant health outcomes using data from a longitudinal cohort study of head-and-neck squamous cell carcinoma patients.}
        \item {Use principles of epidemiology and tools from the fields of nutritional epidemiology, data science, and statistics to develop research questions and analytical strategies for my research projects.}
        \item {Evaluate the role of food insecurity on dietary behaviors and health outcomes in subjects with a history of cancer by employing NHANES data for this arm of my research.}
        \item {Examine the role of food insecurity on health outcomes secondary to COVID-19 in the U.S. using a variety of data sources (USDA, Census Bureau, BEA, AHA, etc.).}
        \item{Mentor dietetic interns on a research project during the research rotation of their dietetic internship.}
        \item{Mentor undergraduate students taking on individual research projects in nutritional epidemiology.}
        \item{Serve as a peer-reviewer for several peer-reviewed journals in the fields of cancer biology and nutritional sciences.}
        \item {Supervisor: Anna Arthur ( \textcolor{navyblue}{\underline{\href{mailto:aarthur4@kumc.edu}{aarthur4@kumc.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Teaching Assistant, CPSC540: Applied Statistical Methods II} % Job title
    {The University of Illinois at Urbana-Champaign \newline Dept. of Crop Sciences } % Organization
    {1102 S. Goodwin Ave \newline AW-101 Turner Hall, MC-046 \newline
    Urbana, IL} % Location
    {Jan. 2021 - Present \newline 15 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hold a 2-hour weekly recitation/computer laboratory session during the Spring semester. }
        \item{Concepts taught are from the experimental design literature and include: linear models and ANOVA, block designs, variations of Latin Squares, logistic regression, and multilevel linear regression.}
        \item {Practice and increase the students’ familiarity with common statistical software packages (R and SAS, predominantly) through guided sessions that involve application of statistical concepts in software and an introduction to coding/programming.}
        \item{Teach practical skills in RStudio (e.g., statistical analysis, data management with \textit{dplyr}, plotting with \textit{ggplot2}, and R Markdown for clarity of presentation).}
        \item {Other responsibilities include: holding office hours (1 hour, weekly), grading weekly assigned homework, formulating exam questions, grading exams, and leading lectures in place of the absent professor.}
        \item {Supervisor: Alexander Lipka ( \textcolor{navyblue}{\underline{\href{mailto:alipka@illinois.edu}{alipka@illinois.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Data Analyst}% Job title
    {Champaign Public Health District } % Organization
    {201 W. Kenyon Rd. \newline
    Champaign, IL} % Location
    {Feb. 2021 - Jul. 2021 \newline 8 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and analyzed survey data for a stakeholder analysis evaluating interest and feasibility of farm to school programs in school districts within the Champaign-Urbana region.}
        \item{Led the data management and analysis arm of the project.}
        \item{Prepared plots for a public presentation in \textit{ggplot2}.}
        \item{Prepared and delivered a public presentation on the results of the analysis.}
        \item {Supervisor: Jennifer Lotton \textcolor{navyblue}{\underline{\href{mailto:jlotton@c-uphd.org}{jlotton@c-uphd.org}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------

  \cventry
    {Teaching Assistant, CPSC440: Applied Statistical Methods I} % Job title
    {The University of Illinois at Urbana-Champaign \newline Dept. of Crop Sciences } % Organization
    {1102 S. Goodwin Ave \newline AW-101 Turner Hall, MC-046 \newline
    Urbana, IL} % Location
    {Jan. 2019 - Present \newline 20 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hold one 2-hour weekly recitation/computer laboratory session where I lecture and lead review statistical concepts learned in the lecture component for up to 80 students.}
        \item {Practice and increase the students’ familiarity with common statistical software packages (R and SAS, predominantly) through guided sessions that involve application of statistical concepts in software and an introduction to coding/programming.}
        \item {Other responsibilities include: holding office hours (2 hours, weekly), grading weekly assigned homework, grading weekly quizzes, formulating exam questions, grading exams, and leading lectures in place of the absent professor.}
        \item {Supervisor: Alexander Lipka ( \textcolor{navyblue}{\underline{\href{mailto:alipka@illinois.edu}{alipka@illinois.edu}}})}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Contributing Author, Nutrition and Wellness Resources } % Job title
    {The Military Families Learning Network } % Organization
    {905 S. Goodwin \newline 343 Bevier Hall \newline
    Urbana, IL} % Location
    {Aug. 2018 - Sep. 2021 \newline 10 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared evidence-based blog-posts concerning relevant and contemporary nutrition topics, ranging from different types of diets to describing nutrients of concern.}
        \item {Translated scientific literature into comprehensible discourse targeted for a lay audience, comprised predominantly of military service professionals and their families.}
        \item {Supervisor: Karen Chapman-Novakofski \textcolor{navyblue}{\underline{\href{mailto:kmc@illinois.edu}{kmc@illinois.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Biochemistry Tutor} % Job title
    {Freelance} % Organization
    {College Park, MD} % Location
    {Oct. 2017 - Aug. 2018 \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored and mentored undergraduate students who sought additional help with coursework in biochemistry, metabolism, biology, or physiology at the University of Maryland, College Park.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Nutrition Educator/Grocery Store Tour Leader } % Job title
    {The Manna Food Center } % Organization
    {9311 Gaither Road \newline
Gaithersburg, MD} % Location
    {Jun. 2016 - Aug. 2018 \newline 10 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led free nutrition classes at various grocery store settings in Montgomery County, primarily to a low socioeconomic-status (SES) audience.}
        \item {Implemented my background and proficiency in nutrition to communicate optimal methods for consuming healthy foods (to prevent chronic illness) while on a strict budget.}
        \item {Supervisor: Jackie DeCarloi \textcolor{navyblue}{\underline{\href{mailto:jackie@mannafood.org}{jackie@mannafood.org}}})}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {The University of Maryland, Dept. of Kinesiology} % Organization
    {4200 Valley Drive \newline Suite 2242 \newline College Park, MD} % Location
    {Sep. 2017 - Dec. 2017 \newline 20 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Discerned the role of calcium (Ca2+) and sodium (Na+) transport and downstream metabolic/energetic implications in both normal/healthy and compromised (heart failure) cardiac mitochondrial models.}
        \item{Employed SDS-Page and Western Blot in my methodology.}
        \item{Supervisor: Sarah Kuzmiak-Glancy
        {\underline{\href{mailto:sglancy@umd.edu}{sglancy@umd.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {getFRUVED Healthy Campus Environmental Audit (HCEA) } % Job title
    {The University of Maryland, College Park} % Organization
    {College Park, MD} % Location
    {Aug. 2017 - Dec. 2017 \newline 10 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Audited the food/dining services, built, and natural environments that serve the ~37,000 students attending the University of Maryland using a survey methodology.}
        \item{Supervisor: Margaret Udahogora
        {\underline{\href{mailto:mudahogo@umd.edu}{mudahogo@umd.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Medical Scribe} % Job title
    {Scribe America, LLC and Arthritis and Rheumatism Associates, P.C.} % Organization
    {14995 Shady Grove Road \newline Suite 250 \newline Rockville, MD} % Location
    {May. 2016 - Jun. 2017 \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as the personal medical scribe for Dr. Evan Siegel MD.}
        \item{Tasks included precise and real-time documentation of patient history, physical exam findings, medical decision-making, differential diagnoses as well as the ordering of lab orders, diagnostic imaging, and assignment of billing codes for each patient encounter.}
        \item{Attended several lectures/seminars led by Dr. Siegel and other physicians on the treatment and care of patients with rheumatoid arthritis, psoriatic arthritis, and ankylosing spondylitis with appropriate medical interventions.}
        \item{Supervisor: Evan Siegel}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Institute for Bioscience and Biotechnology Research (IBBR) } % Organization
    {9600 Gudelsky Dr. \newline
Rockville, MD} % Location
    {Feb. 2016 - Jun. 2016 \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed compounds (fumagillin derivatives) for the treatment of acute giardiasis.}
        \item{Implemented protein purification, enzymatic kinetics assays, bacterial transformation, crystallization/structure resolution, and compound-target characterization as the primary methodological tools.}
        \item{Supervisor: Oznat Herzberg
        {\underline{\href{mailto:oznat@umd.edu}{oznat@umd.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {The University of Maryland, Dept. of Nutrition and Food Science} % Organization
    {0112 Skinner Building \newline
University of Maryland, College Park \newline
College Park, MD} % Location
    {Jan. 2015 - May. 2015 \newline 10 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Studied the dose-dependent effects of folic acid on colorectal carcinogenesis and colorectal cancer chemoprevention. Methods employed: cell culture, MTT assay, SDS-PAGE, and western blot}
        \item{Supervisor: Seong-Ho Lee
        {\underline{\href{mailto:slee2000@umd.edu}{slee2000@umd.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Emergency Department Medical Scribe} % Job title
    {Scribe America, LLC } % Organizat ion
    {Doctors Community Hospital \newline
8118 Good Luck Rd \newline
Lanham, MD
} % Location
    {Nov. 2014 - Mar. 2015 \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Aided Emergency Department physicians and nurse practitioners accurately document patient visit and chart information.}
        \item{Carried out precise and real-time documentation of patient history.}
        \item{Recorded physical exam findings, medical decision-making, differential diagnoses, and prepared patients for Emergency Department discharge or hospital admission, as instructed by the attending physician.}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {
Summer Research Fellow (Pharmacological Sciences Summer Diversity Program) }% Job title
    {The University of Washington, Dept. of Pharmaceutics  } % Organizat ion
    {H272 Health Science Building \newline
Box 357610 \newline
Seattle, WA
} % Location
    {Nov. 2014 - Mar. 2015 \newline 40 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized novel compounds targeted for ALDH1a2 inhibition; suppression of retinoic acid biosynthesis.}
        \item{Specific tasks included conducting compound synthesis and characterization via 1H-NMR and Mass Spectrometry.}
        \item{collected kinetic data for the synthesized compounds to test their efficacy by conducting in-vitro experiments.}
        \item{assisted with pharmacokinetic studies in mice.}
         \item{Supervisor: John Amory
        {\underline{\href{mailto:jamory@uw.edu}{jamory@uw.edu}}})}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Emergency Department Medical Scribe} % Job title
    {Scribe America, LLC } % Organizat ion
    {INOVA Mt. Vernon Hospital \newline
2501 Parkers Ln. \newline
Alexandria, VA
} % Location
    {May. 2013 - Nov. 2013  \newline 30 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Aided Emergency Department physicians and nurse practitioners accurately document patient visit and chart information.}
        \item{Carried out precise and real-time documentation of patient history.}
        \item{Recorded physical exam findings, medical decision-making, differential diagnoses, and prepared patients for Emergency Department discharge or hospital admission, as instructed by the attending physician.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {The University of Maryland, Dept. of Nutrition and Food Science} % Organization
    {0112 Skinner Building \newline
University of Maryland, College Park \newline
College Park, MD} % Location
    {Aug. 2012 - Feb. 2013 \newline 15 hrs/week} % Dates and time
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tested the hypothesis that preadipocyte senescence is mediated by ATM and DNA-PKCS by conducting in vitro experiments.}
        \item{Employed techniques included cell culture, fluorescence microscopy, flow cytometry, and Oil-Red-O staining.}
         \item{Supervisor: Caroline Rocourt}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
