%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Smith RL, Gany F, Arthur AE. County-level Food Insecurity and COVID-19 Mortality: An Ecological Analysis. 2022. (Manuscript in preparation for publication).} % Pub


%---------------------------------------------------------
  
   \cvskill
    {} % leave empty
    {Palsgaard P, \textbf{Maino Vieytes CA}, Peterson N, Francis SL,Monroe-Lord L, Sahyoun N, Ventura-Marra M, Weidauer L, Xu F, Arthur AE. Modeling Health Professionals' Views and Knowledge of the Aging Process. (Submitted for publication)} % Pub

%---------------------------------------------------------

 \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Zhu R, Gany F, Burton-Obanla A, Arthur AE. Empirical Dietary Patterns Associated with Food Insecurity in U.S. Cancer Survivors: NHANES 1999-2018. International Journal of Environmental Research and Public Health. 2022, 18, 14062. doi: 10.3390/ ijerph192114062.} % Pub


%---------------------------------------------------------

  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Rodriguez-Zas SL, Madak-Erdogan Z, Smith RL, Zarins KR, Wolf GT, Rozek, LS, Mondul, AM, Arthur AE. Adherence to a priori-defined Diet Quality Indices Throughout the Early Disease Course is Associated with Survival in Head and Neck Cancer Survivors: An Application Involving Marginal Structural Models. Frontiers in Nutrition. 2022, 9, 791141.doi: 10.3389/fnut.2022.791141.} % Pub


%---------------------------------------------------------

  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Mondul AM, Crowder SL, Zarins KR, Edwards CG, Davis EC, Wolf GT, Rozek LS, Arthur AE. Pretreatment Adherence to a priori-Defined Dietary Patterns Is Associated with Decreased Nutrition Impact Symptom Burden in Head and Neck Cancer Survivors. Nutrients. 2021, 13, 3149. doi: 10.3390/nu13093149.} % Pub


%---------------------------------------------------------

  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Mondul AM, Zarins KR, Wolf GT, Rozek LS, Arthur AE. Associations Between a Priori-Defined Diet Quality Indices and Survival in a Longitudinal Cohort Study of Head and Neck Squamous Cell Carcinoma Patients. Current Developments in Nutrition. 2020, 4, Issue Supplement 2, 336. doi: .} % Pub


%---------------------------------------------------------

  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Mondul AM, Li Z, Zarins KR, Wolf GT, Rozek LS, Arthur AE. Dietary Fiber, Whole Grains, and Head and Neck Cancer Prognosis: Findings from a Prospective Cohort Study. Nutrients. 2019, 11 (10), 2304. doi: 10.3390/nu11102304.} % Pub


%---------------------------------------------------------

  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes CA}, Taha HM, Burton-Obanla AA, Douglas KG, Arthur AE. Carbohydrate Nutrition and the Risk of Cancer. Current Nutrition Reports. 2019, 8, 230-239. doi: 10.1007/s13668-019-0264-3.} % Pub



  %---------------------------------------------------------
  \cvskill
    {} % leave empty
    {\textbf{Maino Vieytes, CA}, Amory JK. Aldehyde Dehydrogenase-1A2: A Target for Male Contraception. 2014 SACNAS National Conference: Research Presentation Abstracts. FRI-331.} % Pub


%---------------------------------------------------------
\end{cvskills}

